Supplimental: A System of Equations and Derivation of Sparse Constant-Pressure\slash Constant-Volume Chemical Kinetic Jacobians for \texttt{pyJac}

### 2018-05-31 derivations.tex
mark as supplimental

\title{A System of Equations and Derivation of Sparse Constant-Pressure\slash Constant-Volume Chemical Kinetic Jacobians for \texttt{pyJac}}

@@

%====================================================================
\begin{abstract} % not to exceed 200 words
This document presents the system of chemical kinetic equations evaluated by the new version of code-generation platform, \texttt{pyJac-v2}.
First, the thermo-chemical source terms for fixed-mass, adiabatic constant-pressure\slash constant-volume (\conp/\slash\conv/) reactors are given, followed by the derivation of the sparse analytical chemical kinetic Jacobian for both reactors.
Finally, the resulting Jacobian equations are summarized using a generalized notation for a quick-reference.
\end{abstract}

@@

\section{Introduction}
This document contains the derivations for \texttt{pyJac} v2.0, which generates code to evaluate the chemical source terms and analytical chemical kinetic Jacobians of constant-pressure\slash constant-volume, fixed-mass, adiabatic reactors.
Note that equations specific to the constant-pressure or constant-volume derivation will be marked with \conp/ or \conv/ respectively.
The derivations in this document based upon the output of the script \href{https://github.com/arghdos/SPyJac-paper/blob/master/derivations/scripts/derivations.py}{derivations.py} in the GitHub repository for this paper.
This script depends on the symbolic mathematics library SymPy~\cite{sympy}, and was tested with versions 1.0 and 1.1.1

>>>>

\title{Supplimental: A System of Equations and Derivation of Sparse Constant-Pressure\slash Constant-Volume Chemical Kinetic Jacobians for \texttt{pyJac}}

@@

%====================================================================
\begin{abstract} % not to exceed 200 words
This document is a suppliment to the work, \textit{SIMD\slash SIMT-vectorized Sparse Chemical Kinetic Jacobian\slash Thermo-chemical Source-Term Evaluation} and presents the system of chemical kinetic equations evaluated by the new version of code-generation platform, \texttt{pyJac-v2}.
First, the thermo-chemical source terms for fixed-mass, adiabatic constant-pressure\slash constant-volume (\conp/\slash\conv/) reactors are given, followed by the derivation of the sparse analytical chemical kinetic Jacobian for both reactors.
Finally, the resulting Jacobian equations are summarized using a generalized notation for a quick-reference.
\end{abstract}

@@

\section{Introduction}
This document is a suppliment to the paper---\textit{SIMD\slash SIMT-vectorized Sparse Chemical Kinetic Jacobian\slash Thermo-chemical Source-Term Evaluation}---and is provided as a reference guide to the equations evaluated by \texttt{pyJac} v2.0, a code-generation platform for the evaluatation of chemical source terms and analytical chemical kinetic Jacobians of constant-pressure\slash constant-volume, fixed-mass, adiabatic reactors.
Note that equations specific to the constant-pressure or constant-volume derivation will be marked with \conp/ or \conv/ respectively.
The derivations in this document based upon the output of the script \href{https://github.com/arghdos/SPyJac-paper/blob/master/derivations/scripts/derivations.py}{derivations.py} in the GitHub repository for this paper.
This script depends on the symbolic mathematics library SymPy~\cite{sympy}, and was tested with versions 1.0 and 1.1.1
